---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We have the following options to store configurations:

* Using environment variables: This is dangerous (no namespacing), inflexible
  (global settings), just strings, very inflexible data structure.

* Using R options: kind of hidden, one setting for each R session, very flexible
  data structure, R native. Cannot be used for other programming langauges.

* config file: transparent, portable, somehow flexible data structure. Using
  working directory as reference, allows for heuristics like various profile 
  files. Language agnostic.

We believe a config file is best suited. Use something like reprex:::opts() as
default arguements of `style_dir()`

```{r, eval = FALSE}
style_dir(
  path = fallback("."),
  ...,
  style = fallback("tidyverse_style"),
  transformers = style(...),
  filetype = fallback("R"),
  recursive = fallback(TRUE),
  exclude_files = fallback(NULL),
  include_roxygen_examples = fallback(TRUE)
)
```

There are different options as per how this could be implemented on the 
config file part.

- storing *all* configurations in one file `fallback.yaml` and use sub-headers 
  for the different packages. Advantage: All configurations in one place.
  
- create a separate file for each package, e.g. `styler.yaml` to store styler
  configurations. Drawback: Directory convolution. Solution: use folder fallback.
